
\documentclass{beamer}
\usetheme{Madrid}

\title{Emergency Response Scenarios}
\subtitle{CPR \& AED Training}
\author{Prince of Songkla University}
\date{\today}

\begin{document}

\frame{\titlepage}

% Scenario 1
\begin{frame}
\frametitle{Scenario 1}
Students and friends represent the university at the "Play and Preserve the Environment" project in collaboration with the Health Promotion Foundation at Patong Beach. A 67-year-old Thai man is observed with a pale face, staggering, then collapsing to the ground. Bystanders are shocked but do not assist. 

\textbf{How should the student respond to this emergency?}
\end{frame}

% Scenario 2
\begin{frame}
\frametitle{Scenario 2}
Students participate in the Super Sports Laguna Phuket Marathon, promoting health and reducing environmental impact (carbon footprint). A 55-year-old Thai woman collapses face down after picking up a bottle off the ground at the 4 km mark, in front of the Laguna Holiday Club Phuket Resort. Bystanders are alarmed but do nothing.

\textbf{How should the students respond?}
\end{frame}

% Scenario 3
\begin{frame}
\frametitle{Scenario 3}
During a student activity hour, while heading to a community service event at the Computer College Student Club, students decide to buy coffee. A 65-year-old male parent of a fellow student collapses and becomes unconscious.

\textbf{How should the students respond?}
\end{frame}

% Scenario 4
\begin{frame}
\frametitle{Scenario 4}
A health-conscious student regularly exercises at the PSU Phuket Sport Complex. Passing by the performing arts room, a crowd is observed around a 45-year-old woman lying unconscious on the floor.

\textbf{How should the student respond?}
\end{frame}

\end{document}
