\documentclass{article}
\usepackage[utf8]{inputenc}

% Add one of these packages to allow URLs and long text to wrap properly:
%  - \usepackage[hyphens]{url}  % basic URL wrapping
\usepackage{url}          % extended URL wrapping
%\usepackage[hyphens]{url}

% (Optional) Improve spacing and hyphenation:
\usepackage{microtype}
\sloppy  % relax LaTeX's strict spacing rules to help avoid overfull lines

\begin{document}

\section{Overview}
Prince of Songkla University (PSU) provides a free email service to all students, faculty, and staff through Microsoft 365 (Outlook). This PSU email account allows users to communicate and share information all in one place, and it can be accessed via the website \url{https://email.psu.ac.th} or through a mobile email application.

\section{Features}
The PSU email service offers a rich set of features:
\begin{itemize}
    \item \textbf{Email:} Send and receive important communications with your PSU email account.
    \item \textbf{Calendar:} Manage appointments, class schedules, and events efficiently.
    \item \textbf{Contacts:} Easily find and contact important individuals within the university.
    \item \textbf{Email Forwarding:} Optionally forward your PSU emails to a personal email address for convenience.
    \item \textbf{Email Client Support:} Access PSU email through email client applications (e.g. Outlook) on your computer or mobile device.
\end{itemize}

\section{Storage Quota}
Each PSU email account comes with a total storage allocation (shared between email and OneDrive cloud storage) as follows:
\begin{itemize}
    \item Students: \textbf{4 GB} total storage
    \item Staff: \textbf{10 GB} total storage
    \item Faculty: \textbf{30 GB} total storage
\end{itemize}
This total storage is divided into:
\begin{itemize}
    \item \textit{Outlook Email Storage:} for storing emails and attachments.
    \item \textit{OneDrive Storage:} for storing documents, images, videos, and other files.
\end{itemize}
You can check used and remaining storage by logging into OneDrive with your PSU account at \url{https://onedrive.live.com}.

\section{Accessing PSU Email (Microsoft 365 Outlook)}
Follow these steps to access your PSU email:

\begin{enumerate}
    \item \textbf{Enable Two-Step Authentication (2FA) for Security:}
    \begin{itemize}
        \item Download and install the Microsoft Authenticator app on your smartphone.
        \item Set up two-step authentication for your PSU account using the Microsoft Authenticator app. For details, visit \url{https://sysadmin.psu.ac.th/2022/11/04/microsoft-authenticator}.
    \end{itemize}

    \item \textbf{Log in to PSU Email:}
    \begin{itemize}
        \item Open a web browser and go to \url{https://email.psu.ac.th}.
        \item Enter your PSU email address (username) and your PSU Passport password.
        \item Click the ``Sign In'' button.
    \end{itemize}
    \textit{Note: Your PSU Passport password is the same one used for PSU systems like SIS or MIS-DSS.}

    \textbf{Username Format Examples:}
    \begin{itemize}
        \item \textit{Students admitted in 2024 or later:} \texttt{<StudentID>@psu.ac.th} 
        \item \textit{Students admitted in 2021--2023:} \texttt{<StudentID>@email.psu.ac.th}
        \item \textit{Faculty and Staff:} \texttt{<PSU Passport username>@psu.ac.th}
    \end{itemize}
\end{enumerate}

\textbf{Important:} Do \emph{not} uninstall the Microsoft Authenticator app after setup. 
Removing it may lock you out of your PSU email account.

\section{Frequently Asked Questions (FAQ)}
\begin{description}
    \item[Q: I forgot my PSU email/Microsoft 365 password. What should I do?] 
    You can reset your password via the PSU Password Reset system at \url{https://passport.psu.ac.th/index.php?content=forgetpass}.
    \item[Q: How do I change my PSU email/Microsoft 365 password?]
    Visit \url{https://passport.psu.ac.th/index.php?content=changepass}, set a new password, then wait about 15 minutes before logging in with the new password.
    \item[Q: I changed my phone or removed Microsoft Authenticator. How to set up 2FA again?] 
    Contact the DIIS staff to reset your two-step authentication. 
    After that, reconfigure Microsoft Authenticator on your new phone.
    \item[Q: How long can students use their PSU account?]
    Students can use PSU Microsoft 365 during enrollment, and for 6 months after graduation.
    \item[Q: How long can faculty/staff use their PSU account?]
    Faculty/staff can use PSU Microsoft 365 during employment. If leaving before retirement, the account remains active for 6 months. Retirees keep the account indefinitely.
\end{description}

\section{Support}
If you need help, please contact PSU Digital Innovation and Intelligent Systems Office (DIIS):
\begin{itemize}
    \item \textbf{Phone:} 0-7428-2082 or 0-7428-2128
    \item \textbf{Email:} \url{passport@psu.ac.th}
\end{itemize}

\end{document}